\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{charter}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.2in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{4.5pt}

\titleformat{\section}{
  \bfseries\large\raggedright
}{}{0em}{}[\titlerule]

\newcommand{\resumeItem}[1]{\item \small{#1}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in, label=\textbullet]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Prashant Singhal} \\ \vspace{4pt}
    Bengaluru, India $|$ +91-8124160275 $|$ \href{mailto:6prashant1singhal9@gmail.com}{6prashant1singhal9@gmail.com} $|$ 
    \href{https://linkedin.com/in/prashant-singhal-18ab819b}{linkedin.com/in/prashant-singhal-18ab819b}
\end{center}

\vspace{-6pt}

\begin{center}
\textbf{\large Senior Frontend Engineer / Frontend Engineering Lead} \\
React.js \textbar\ TypeScript \textbar\ System Design
\end{center}

\section{Summary}
Frontend Engineer with $\sim$7 years of experience building large-scale, enterprise AI-first SaaS products. Proven expertise in React.js, TypeScript, complex state management, frontend architecture, and scalable UI systems. Built and scaled real-time, multi-channel communication platforms across WhatsApp, RCS, SMS, Web, Mobile Push, and Voice integrations. Strong product mindset with a focus on delivery, performance optimization (Core Web Vitals), accessibility, scalability, and code quality. Experienced in designing scalable frontend architectures and driving system design decisions. Leveraged AI-assisted development tools to improve development velocity, debugging efficiency, and developer experience.

\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Commotion Inc., Mumbai}{}{Frontend Engineering Lead}{Aug 2025 - Mar 2026}
\resumeItemListStart
\resumeItem{Co-led development of AI OS ecosystem including AI Copilot, marketing automation, Voice AI agent, and Agentic AI worker orchestration, contributing to a 51\% stake acquisition by Tata Communications (\$25M).}
\resumeItem{Guided architecture and delivery of an AI-enabled mass communication platform (SMS, Email, Push) using React.js, TypeScript, REST APIs, TanStack Query, and Zustand, integrating into an enterprise codebase; accelerated Phase 1 delivery by 40\% (1.5 months faster than client team) using AI-assisted development and Figma MCP workflows.}
\resumeItem{Drove key decisions on frontend microservices architecture and scalable frontend system design, integrating analytics SDKs, AI Copilot, and Node.js based template exporter; owned maintenance of frontend microservices, freeing the bandwidth of 2 engineers.}
\resumeItem{Leveraged AI-assisted development tools (Claude Code) using structured planning and review workflows, achieving 2x individual productivity and $\sim$1.25x team productivity; drove adoption through measurable outcomes.}
\resumeItem{Partnered cross-functionally with product, design, and backend teams to drive product roadmap, UX quality, and frontend architecture decisions across 3 core features.}
\resumeItem{Introduced Jest-based testing standards, CI/CD checks, and Git hooks, increasing test coverage from 32\% to 87\% and reducing regression bugs to near zero in production.}
\resumeItem{Built a Voice AI transcription and TTS POC, benchmarking multiple providers against an in-house system; contributed to a Voice AI agent showcased at Global AI Summit 2026 and ranked in top cohort.}
\resumeItemListEnd

\resumeSubheading
{}{ }{Senior Frontend Engineer}{Jan 2023 - Aug 2025}
\resumeItemListStart
\resumeItem{Led a 10-member engineering team in a high-impact 14-day RCS sprint, delivering full-channel integration 4x faster than competing platforms under strict timelines.}
\resumeItem{Directed frontend architecture and development for an AI-first multi-channel SaaS platform using React.js, TypeScript, and scalable component architecture, supporting Marketing and Care use cases and contributing to 10x company growth and major revenue deals.}
\resumeItem{Owned end-to-end frontend integrations across WhatsApp, SMS/MMS, RCS, Web Push, Mobile/In-App Push, AI Voice IVR, Instagram, and Facebook using REST APIs and event-driven architecture (10+ customer touchpoints).}
\resumeItem{Mentored engineers, provided architectural guidance, and enforced strong ownership and delivery standards across the team.}
\resumeItem{Architected and built AI-powered chatbot and goal-based user journeys across multiple channels using React.js and scalable UI patterns.}
\resumeItem{Designed and built a real-time ticketing system (Care Agent Console) using WebSockets and React.js, including a data merging algorithm for unified communication streams, a dynamic widget framework, and an AI Copilot; improved query resolution speed by 30\%.}
\resumeItem{Built a scalable Component \& Template Builder enabling dynamic message creation and AI-driven personalisation; designed a variable support system and reconciliation algorithm scalable across channels.}
\resumeItem{Developed a JavaScript-based AI Copilot SDK (AI Concierge) with dynamic component rendering and event-driven architecture, increasing customer engagement by 30\%.}
\resumeItem{Standardised repetitive workflows such as testing, boilerplate generation, refactoring, and state management using AI-assisted processes, improving development velocity by up to 20\%.}
\resumeItem{Built an Instagram-like content reel with product tagging and PDP integration using Preact, Redux, and SCSS, achieving $\sim$80\% smaller bundle size and enabling partnerships with clients like PUMA, Walmart, and Target.}
\resumeItemListEnd

\resumeSubheading
{Fudr, Jaipur}{}{Senior Frontend Engineer}{Jan 2021 - Dec 2022}
\resumeItemListStart
\resumeItem{Delivered responsive, high-performance UIs with strong attention to UX and business workflows. Improved Lighthouse score for the Enterprise app from 72 to 94, and the client-facing app from 77 to 95.}
\resumeItem{Worked closely with stakeholders to define MVPs and iterate rapidly based on user feedback, helping onboard 800+ clients and generate \$75K+ annual revenue.}
\resumeItem{Implemented Progressive Web Application (PWA) using Service Workers and Web Workers to enable push notifications, increasing user engagement by 80\%.}
\resumeItem{Integrated Google Analytics SDK to track usage metrics and derive 10+ actionable customer insights.}
\resumeItemListEnd

\resumeSubheading
{}{ }{Frontend Developer}{May 2020 - Dec 2020}
\resumeItemListStart
\resumeItem{Built and scaled frontend applications for F\&B operations, marketing, and loyalty platforms, increasing weekly active users from 100 to 75K.}
\resumeItem{Set up CI/CD pipelines across repositories, reducing commit-to-production time by 50\% and improving release reliability.}
\resumeItemListEnd

\resumeSubheading
{Freelance, Jaipur}{}{Frontend Developer}{Jul 2019 - Apr 2020}
\resumeItemListStart
\resumeItem{Worked with global clients to gather requirements via JIRA, negotiate timelines, and deliver production-grade frontend solutions.}
\resumeItem{Provided technical consultancy and improved delivery timelines by 25\% through structured development workflows and milestone reviews.}
\resumeItemListEnd

\resumeSubheading
{QED42 Engineering Pvt Ltd, Pune}{}{Full Stack Developer}{Jan 2016 - Apr 2017}
\resumeItemListStart
\resumeItem{Contributed to Drupal Commerce Shippo (open-source logistics module), improving organisation contribution metrics by 10\%.}
\resumeItem{Developed frontend and backend features using Drupal (PHP) and JavaScript for enterprise clients including Nestle, contributing to $\sim$40\% revenue growth.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Skills}
\small{
\textbf{Core:} React.js, TypeScript, JavaScript (ES6+), Frontend Architecture, System Design, REST APIs, Web Performance Optimization, Core Web Vitals \\
\textbf{Frontend:} HTML5, CSS3, Preact, Redux, SCSS, Tailwind CSS, Zustand, TanStack Query \\
\textbf{Architecture:} Scalable UI Systems, Component Architecture, Micro Frontends \\
\textbf{APIs \& Data:} GraphQL, JSON, SSE, WebSockets \\
\textbf{Testing \& Quality:} Jest, Unit Testing, Integration Testing, Accessibility, WCAG, Cross-browser Compatibility \\
\textbf{Tools \& Platforms:} CI/CD, Docker, Git, Git Hooks, Figma, Webpack, Vite, Rollup, NPM, Yarn, AWS, Azure, GCP, GitHub Actions \\
\textbf{Practices:} Agile/Scrum, Clean Code, Code Reviews, Documentation, JIRA \\
\textbf{Backend:} Node.js, PHP \\
\textbf{AI-Assisted Development:} AI-assisted Debugging, AI Copilots (Claude Code, GitHub Copilot), Claude Skills, MCP Servers
}

\section{Education}
Bachelor of Technology (B.Tech) - Information Technology \\
Vellore Institute of Technology \hfill 2012 - 2016

\end{document}
